\documentclass[a4paper,11pt]{article}
\usepackage{focusframe}
%TC:subst \frsect \section  
%TC:subst \frsubsect \subsection  

\edef\xjobname{WilliamBlack-poctest}


    
    
\title{Animation Translation of the Japanese Nation}
\date{Date of last edit: \today}
\author{William Black 42920477}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

\begin{document}


\tableofcontents

\textbf{\maketitle}
\marginnote{\frfile{3000}}



\frsect{Background and Literature Review}{400}

Here is a few sentences for the frame to count. This is the background of the subject. It includes a literature reviews. Literature reviews are possibly my least favourite part of writing research.




\frsect{Second Section}{100}

We do need two sections to test with... 
Adding words because I'm bloody blind.

Here are some more sentences to take the word count up to 120 for this section. Here are some more sentences to take the word count up to 120 for this section. Here are some more sentences to take the word count up to 120 for this section. Here are some more sentences to take the word count up to 120 for this section. Here are some more sentences to take the word count up to 120 for this section. Here are some more sentences to take the word count up to 120 for this section. Here are some more sentences to take the word count up to 120 for this section.

\frsect{Contentfree Section}{200}

\frsubsect{Leading Paragraph}{100}

Translation is a tricky business, you see, ever since time immemorial translators have wondered etc. Here is more text for a leading paragraph. Why on earth does the header appear twice in this paragraph? No one knows, it is an enigma. Here are some more sentences to take the word count up to 100 or so. Here are some more sentences to take the word count up to 100 or so. Here are some more sentences to take the word count up to 100 or so. Here are some more sentences to take the word count up to 100 or so. And finally just one more sentence if you please thank you.



\frsubsect{Header}{100}

Here are some more sentences to take the word count up to 100 or so. Here are some more sentences to take the word count up to 100 or so. Here are some more sentences to take the word count up to 100 or so. Here are some more sentences to take the word count up to 100 or so. Here are some more sentences to take the word count up to 100 or so. Here are some more sentences to take the word count up to 100 or so. 



\frsect{Explanatory Section}{200}

The reason the subcount is 64 instead of 61, a couple of extra words on top of the main text in the section, is because the subcount includes the words in the heading of the section and the number of the section. This doesn't need to be fixed, as words in the header do usually count as words in the document. 




\frsubsect{Test Subsection}{50}

asdf asdf asdf. why would it work on sections and then not work on subsections. Oh well it seems to be working now. Oh I see, it's counting the number of the subsection too, even though the number is just unfortunately invisible to the user.


\frsubsect{subsectionname}{50}

But there's a new problem here, because the subcount of the section is not updating to include subsections. Darn it. 


\frsect{Theme Background - identify gap}{500}

\frsubsect{what's a translation}{100}

A translation transforms the devil into el diablo. %\lipsum[1]

\frsubsect{what's equivalence}{100}

Equivalence is about getting the word right and also getting the vibe right. %\lipsum[1]

\frsubsect{what's a sign}{100}

\frsubsect{what's a connotative sign}{100}

% \frsubsect{what's the difference between connotative and denotative signs}{100}


% \frsect{Aims}{300}
% \frsubsect{Research Aims}{100}
% \frsubsect{Project Scope}{100}
% \frsubsect{Limitations}{100}

\end{document}